Earth_microbiome_MS

### 2019-07-15 Earth_microbiome_MS.Rmd
updated

#libraries for data processing and formatting
	library(foreign)
	library(stargazer)
	library(psych)
	library(plyr)
	library(xtable)
	library(car) #

@@

```{r Taxonomic filtering}
#Methods obtained from Callahan et al.

@@

#Create table showing the phyla present in the table 
table(tax_table(githubdata_phyloseq)[, "Phylum"], exclude = NULL)
#It is noted here that some phyla are named following a different denomination system

#Remove unchar

@@

#READ ME

@@

Some of the phyla in the table

>>>>

#libraries for data processing and formatting
	library(foreign)
	library(stargazer)
	library(githubdata_phyloseqych)
	library(plyr)
	library(xtable)
	library(car) #

@@

#Taxonomic filtering
```{r Taxonomic filtering}
#Methods obtained from Callahan et al.

@@

#Create table showing the phyla present in the table 
table(tax_table(githubdata_phyloseq)[, "Phylum"], exclude = NULL)
#It is noted here that some phyla are named following a different convention

#Remove ambiguous phyla (if any)
githubdata_phyloseq <- subset_taxa(githubdata_phyloseq, !is.na(Phylum) & !Phylum %in% c("", "uncharacterized"))

#Compute prevalence of each Phyla, store as data.frame
prevdf = apply(X = otu_table(githubdata_phyloseq),
               MARGIN = ifelse(taxa_are_rows(githubdata_phyloseq), yes = 1, no = 2),
               FUN = function(x){sum(x > 0)})

#Add taxonomy and total read counts to this data.frame
prevdf = data.frame(Prevalence = prevdf,
                    TotalAbundance = taxa_sums(githubdata_phyloseq),
                    tax_table(githubdata_phyloseq))

#Create table dispaying the average prevalence of each phyla per sample and the total reads for all phyla in the data frame
plyr::ddply(prevdf, "Phylum", function(df1){cbind(mean(df1$Prevalence),sum(df1$Prevalence))})

@@

#READ ME - Problems encountered

@@

Some of the phyla in the table are named following a differenct convention. If this file is used for the data this will have to be kept in mind. It is possible that other files for EMP data also share this problem.
